\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-12 papers/jss/article.Rnw
words
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@758 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

The same method can also be used to serialize messages to files :

@@

\texttt{serialize} can also be used in a more traditional
object oriented fashion using the dollar operator :

>>>>

The same method can be used to serialize messages to files :

@@

\texttt{serialize} can also be called in a more traditional
object oriented fashion using the dollar operator:
